---
title: "LVAD Patients"
author: "Brian Gulbis, PharmD, BCPS"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, wwarning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(readxl)
library(broom)
library(MASS)

df <- read_excel(
    "../data/raw/2019-05_lvad-gib/data_2019-06-13.xlsx",
    skip = 1,
    col_types = c(
        "numeric",
        "numeric",
        "logical",
        "numeric",
        "logical",
        "logical",
        "logical",
        "logical",
        "logical",
        "skip",
        "logical",
        "logical",
        "logical",
        "logical",
        "logical"
    ),
    col_names = c(
        "patient_id",
        "age",
        "female",
        "bmi",
        "afib",
        "cad",
        "dm",
        "cva",
        "low_inr",
        "recur_gi_bleed",
        "pump_thrombosis",
        "isch_cva",
        "pump_thromb_cva",
        "hemor_cva"
    )
)
```

# Univariate Logistic Regression Models

## Recurrent GI Bleed

### Age
```{r}
glm(recur_gi_bleed ~ age, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Female
```{r}
glm(recur_gi_bleed ~ female, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### BMI
```{r}
glm(recur_gi_bleed ~ bmi, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### A.fib
```{r}
glm(recur_gi_bleed ~ afib, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### CAD
```{r}
glm(recur_gi_bleed ~ cad, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### DM
```{r}
glm(recur_gi_bleed ~ dm, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Stroke
```{r}
glm(recur_gi_bleed ~ cva, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Low INR Goal
```{r}
glm(recur_gi_bleed ~ low_inr, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis

### Age
```{r}
glm(pump_thrombosis ~ age, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Female
```{r}
glm(pump_thrombosis ~ female, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### BMI
```{r}
glm(pump_thrombosis ~ bmi, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### A.fib
```{r}
glm(pump_thrombosis ~ afib, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### CAD
```{r}
glm(pump_thrombosis ~ cad, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### DM
```{r}
glm(pump_thrombosis ~ dm, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Stroke
```{r}
glm(pump_thrombosis ~ cva, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Low INR Goal
```{r}
glm(pump_thrombosis ~ low_inr, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Ischemic Stroke

### Age
```{r}
glm(isch_cva ~ age, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Female
```{r}
glm(isch_cva ~ female, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### BMI
```{r}
glm(isch_cva ~ bmi, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### A.fib
```{r}
glm(isch_cva ~ afib, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### CAD
```{r}
glm(isch_cva ~ cad, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### DM
```{r}
glm(isch_cva ~ dm, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Stroke
```{r}
glm(isch_cva ~ cva, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Low INR Goal
```{r}
glm(isch_cva ~ low_inr, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis or Ischemic Stroke

### Age
```{r}
glm(pump_thromb_cva ~ age, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Female
```{r}
glm(pump_thromb_cva ~ female, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### BMI
```{r}
glm(pump_thromb_cva ~ bmi, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### A.fib
```{r}
glm(pump_thromb_cva ~ afib, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### CAD
```{r}
glm(pump_thromb_cva ~ cad, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### DM
```{r}
glm(pump_thromb_cva ~ dm, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Stroke
```{r}
glm(pump_thromb_cva ~ cva, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Low INR Goal
```{r}
glm(pump_thromb_cva ~ low_inr, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Hemorrhagic Stroke

### Age
```{r}
glm(hemor_cva ~ age, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Female
```{r}
glm(hemor_cva ~ female, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### BMI
```{r}
glm(hemor_cva ~ bmi, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### A.fib
```{r}
glm(hemor_cva ~ afib, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### CAD
```{r}
glm(hemor_cva ~ cad, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### DM
```{r}
glm(hemor_cva ~ dm, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Stroke
```{r}
glm(hemor_cva ~ cva, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

### Low INR Goal
```{r}
glm(hemor_cva ~ low_inr, family = "binomial", data = df) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

# Multivariate Regression Models

## Recurrent GI Bleed

```{r}
glm(
    recur_gi_bleed ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis

```{r}
glm(
    pump_thrombosis ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial",
    data = df
) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Ischemic Stroke

```{r}
glm(
    isch_cva ~ age + female + bmi + afib + cad + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis or Ischemic Stroke

```{r}
glm(
    pump_thromb_cva ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Hemorrhagic Stroke

```{r}
glm(
    hemor_cva ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

# Stepwise Regression Models

## Recurrent GI Bleed

```{r}
glm(
    recur_gi_bleed ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    stepAIC(direction = "backward", trace = FALSE) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis

```{r}
glm(
    pump_thrombosis ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    stepAIC(direction = "backward", trace = FALSE) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Ischemic Stroke

```{r}
glm(
    isch_cva ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    stepAIC(direction = "backward", trace = FALSE) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Pump Thrombosis or Ischemic Stroke

```{r}
glm(
    pump_thromb_cva ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    stepAIC(direction = "backward", trace = FALSE) %>%
    tidy(conf.int = TRUE, exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```

## Hemorrhagic Stroke

```{r}
glm(
    hemor_cva ~ age + female + bmi + afib + cad + dm + cva + low_inr, 
    family = "binomial", 
    data = df
) %>%
    stepAIC(direction = "backward", trace = FALSE) %>%
    tidy(exponentiate = TRUE) %>%
    knitr::kable(digits = 3)
```
