---
title: "IV Contrast Agent Forecast"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(fcasthelpr)
library(flexdashboard)

```

```{r}
f <- mbohelpr::set_data_path("admin_requests", "drug_shortages")

pred_days <- read_rds(paste0(f, "final/pred_days.Rds"))
# update_time <- read_rds(paste0(f, "final/update_time.Rds"))
ts_data <- read_rds(paste0(f, "final/ts_data.Rds"))
df_fc_data_ind <- read_rds(paste0(f, "final/df_fc_data_ind.Rds"))
df_fc_data_combo <- read_rds(paste0(f, "final/df_fc_data_combo.Rds"))
```

Iohexol 350/50
=====================================================

```{r}
p <- "iohexol 350 mg/ml 50 ml VL"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 350/100
=====================================================

```{r}
p <- "iohexol 350 mg/ml 100 ml inj"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 350/150
=====================================================

```{r}
p <- "iohexol 350 mg/ml 150 ml INJ"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 300/10
=====================================================

```{r}
p <- "iohexol 300 mg/ml 10 ml inj VL"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 300/50
=====================================================

```{r}
p <- "iohexol 300 mg/ml 50 ml VL"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 300/100
=====================================================

```{r}
p <- "iohexol 300 mg/ml 100 ml INJ (btl)"
```

```{r child="iv_contrast_child.Rmd"}

```

Iohexol 30/150
=====================================================

```{r}
p <- "iohexol 300 mg/ml 150 ml INJ"
```

```{r child="iv_contrast_child.Rmd"}

```


Iodixanol 320/50
=====================================================

```{r}
p <- "iodixanol 320 mg/ml 50 ml VL"
```

```{r child="iv_contrast_child.Rmd"}

```

Iodixanol 320/100
=====================================================

```{r}
p <- "iodixanol 320 mg/ml 100 ml btl"
```

```{r child="iv_contrast_child.Rmd"}

```

Iodixanol 320/150
=====================================================

```{r}
p <- "iodixanol 320 mg/ml 150 ml btl"
```

```{r child="iv_contrast_child.Rmd"}

```

Iodixanol 320/200
=====================================================

```{r}
p <- "iodixanol 320 mg/ml 200 ml"
```

```{r child="iv_contrast_child.Rmd"}

```

About
=====================================================

### About the forecasts

**Data updated through: `r format(max(ts_data$date), "%B %d, %Y")`**

#### Methodology

* Utilization is based on the number of vials removed from Pyxis or sent from pharmacy each day.
* A forecast for the use of each IV contrast product over the next `r pred_days` days is made using an ensemble model. 

#### Forecast models

* An individual forecast is made for each mask using each of the following models: 
    - ARIMA: Auto-Regressive Integrated Moving Average
    - ARIMA_D: Seasonal decomposition of the utilization with an ARIMA forecast then performed on each of the individual components (trend, weekly seasonality, and remainder)
    - ETS: Exponential Smoothing using state space models
        + Hyndman, R.J., Koehler, A.B., Snyder, R.D., and Grose, S.; *International Journal of Forecasting* 2002. 18(3): 439-454
    - ETS_D: Seasonal decomposition of the utilization with an ETS forecast then performed on each of the individual components (trend, weekly seasonality, and remainder)
    - ETS_DA: Seasonal decomposition of the utilization with an ETS forecast performed on the trend and an ARIMA forecast performed on the weekly seasonality and remainder
    - VAR: Vector Auto-Regression
    - VAR_D: Seasonal decomposition of the utilization with an VAR forecast then performed on each of the individual components (trend, weekly seasonality, and remainder)
* An ensemble forecast is then created by averaging the individual forecasts together.
* Forecasts are made for the next `r pred_days` days (denoted by the line) with an 80% prediction interval (there is an 80% probability that the future value will be within the predication interval; denoted by the shaded area).

#### References

* Created with `r R.version.string`
    - `r format(citation(), style = "html")`
* Forecasts created using the following packages:
    - `r format(citation("fable"), style = "html")`
    - `r format(citation("tsibble"), style = "html")`
* Dashboard and visualizations created using the following packages:
    - `r format(citation("flexdashboard"), style = "html")`
    - `r format(citation("plotly"), style = "html")`
    - `r format(citation("tidyverse"), style = "html")`
    - `r format(citation("readxl"), style = "html")`
    - `r format(citation("tibble"), style = "html")`
    - `r format(citation("dplyr"), style = "html")`
    - `r format(citation("tidyr"), style = "html")`
    - `r format(citation("lubridate"), style = "html")`

> Created by Brian Gulbis, PharmD, BCPS (<brian.gulbis@memorialhermann.org>)
